---
title: "Assignment - 2 - Solving LP Using R"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r}

library("lpSolve") #Activating the lpSolve Package
```

To solve the problem we need to define the objective, constraints, direction and constants

Objective Function
$$ \text{The Objective function is to } Max \hspace{.3cm} Z =  420(L_1+L_2+L_3) + 360 (M_1+M_2+M_3) + 300 (S_1+S_2+S_3) $$
$$ \text {which can be written as } Z = 420L_1+360M_1+300S_1+420L_2+360M_2+300S_2+420L_3+360M_3+300S_3$$
Subject to the following constraints

$$ L_1+M_1+S_1 \le 750 $$
$$ L_2+M_2+S_2 \le 900 $$
$$ L_3+M_3+S_3 \le 450 $$
$$ 20L_1+15M_1+12S_1 \le 13000 $$
$$ 20L_2+15M_2+12S_2 \le 12000 $$
$$ 20L_3+15M_3+12S_3 \le 5000 $$
$$ L_1+L_2+L_3 \le 900 $$
$$ M_1+M_2+M_3 \le 1200 $$
$$ S_1+S_2+S_3 \le 750 $$
Non Negativity Constraints
$$ L_1,L_2,L_3,M_1,M_2,M_3,S_1,S_2,S_3 \ge 0 $$
The above constraints can be written as below
$$ L_1+M_1+S_1+0L_2+0M_2+0S_2+0L_3+0M_3+0S_3 \le 750       $$
$$ 0L_1+0M_1+0S_1+L_2+M_2+S_2+0L_3+0M_3+0S_3 \le 900$$
$$ 0L_1+0M_1+0S_1+0L_2+0M_2+0S_2+L_3+M_3+S_3 \le 450$$
$$ 20L_1+15M_1+12S_1+0L_2+0M_2+0S_2+0L_3+0M_3+0S_3 \le 13000 $$
$$ 0L_1+0M_1+0S_1+20L_2+15M_2+12S_2+0L_3+0M_3+0S_3 \le 12000 $$
$$0L_1+0M_1+0S_1+0L_2+0M_2+0S_2+20L_3+15M_3+12S_3 \le 5000 $$
$$L_1+0M_1+0S_1+L_2+0M_2+0S_2+L_3+0M_3+0S_3 \le 900$$
$$0L_1+M_1+0S_1+0L_2+M_2+0S_2+0L_3+M_3+0S_3 \le 1200$$
$$0L_1+0M_1+S_1+0L_2+0M_2+S_2+0L_3+0M_3+S_3 \le 750$$

Coefficients of the Objective Function  
```{r}
profit_coefficients <- c(420,360,300,420,360,300,420,360,300)
```

Defining the Constraints
```{r}
A <- matrix(c(1,1,1,0,0,0,0,0,0,
                  0,0,0,1,1,1,0,0,0,
                  0,0,0,0,0,0,1,1,1,
                  20,15,12,0,0,0,0,0,0,
                  0,0,0,20,15,12,0,0,0,
                  0,0,0,0,0,0,20,15,12,
                  1,0,0,1,0,0,1,0,0,
                  0,1,0,0,1,0,0,1,0,
                  0,0,1,0,0,1,0,0,1), nrow = 9, byrow=T)
```

Defining the Direction of the constraints 
```{r}
Direction <- c('<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=')
```

Defining the constants i.e. the right hand side values
```{r}
Righthandside <- c(750,900,450,13000,12000,5000,900,1200,750)
```

Calling the lp function to solve the problem basing the objective function i.e. to maximize the profits
```{r}
result<-lp('max',profit_coefficients,A,Direction,Righthandside)
```

Calling the lp function again to get the values for the variables defined above
```{r}
lp('max',profit_coefficients,A,Direction,Righthandside)$solution
```
